Gammapy: A Python package for gamma-ray astronomy

### 2022-11-01 src/ms-review.tex
Improve definition of norm

Where the spectral model $F$ implicitly carries the total flux
norm of the model. The spatial model $G$ optionally depends
on energy and allows to support e.g. energy dependent
morphology models. The temporal model component $H$
optionally also supports an energy variable to
allow for spectral variations of the model with time.

@@

The models follow a naming scheme which contains the category as a suffix to
the class name.
The spectral models include a special class of normed models, named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less norm parameter
instead of an amplitude parameter with physical units. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding taking into account
the absorbtion effect on 
\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
model. \gammapy supports a variety of EBL absorbtion models, such as

@@

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps, flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. The norm of the best fit "reference" spectral
model is fitted (or 'scaled') in the  restricted data range only.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
	\caption{Example of a 3D analysis for simulated sources using the \cta \irfs. The
		left image shows a significance map where the three simulated sources can be
		seen. The middle figure shows another significance map, but this time after
		subtracting the best-fit model for each of the sources, which are displayed in
		black. The right figure shows the contribution of each source model to the
		circular region of radius 0.5\textdegree drawn in the left image, together with
		the excess counts inside that region. } \label{fig:cube_analysis}
\end{figure*}

>>>>

Where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
for the total flux of the model. The spatial model $G$ optionally depends
on energy and allows to support e.g. energy dependent
morphology models. The temporal model component $H$
optionally also supports an energy variable to
allow for spectral variations of the model with time.

@@

The models follow a naming scheme which contains the category as a suffix to
the class name. The spectral models include a special class of normed models,
named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less \textit{norm} parameter
instead of an \text{amplitude} parameter with physical units. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding taking into account
the absorbtion effect on 
\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
model. \gammapy supports a variety of EBL absorbtion models, such as

@@

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps, flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. A multiplicative correction factor (the \textit{norm})
is applied to the best fit "reference" spectral
model and is fitted in the restricted data range, defined by the 
bin group, only.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cube_analysis.pdf}
	\caption{Example of a 3D analysis for simulated sources with point-like, Gaussian
		and shell-like morphology. The simulation uses \textit{prod5} \irfs from \cta.
		The left image shows a significance map where the three simulated sources can be
		seen. The middle figure shows another significance map, but this time after
		subtracting the best-fit model for each of the sources, which are displayed in
		black. The right figure shows the contribution of each source model to the
		circular region of radius 0.5\textdegree drawn in the left image, together with
		the excess counts inside that region. } \label{fig:cube_analysis}
\end{figure*}
